Pulling oral and IV data from CvTdb

### 2024-11-04 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Updated object 'cvt' and related documentation. invivPK_loq_units were not ug/mL as intended. Added description of each column of the data. Added description for fup-optimizing clearance aware 1-compartment model in data.R

quick_message(c(
  "Modifying Data:",
  "Converting loq units to concentration unit standard mg/L",
  "Converting concentration units to standard mg/L",
  "Converting concentration sd units to the standard mg/L",
  "Keeping concentration values for series 23340 and 23380 to original records"
))
# Normalize LOQ units
cvt_df <- cvt_df %>%
  mutate(invivPK_loq = if_else(
    invivPK_loq_units %in% c("ug/L", "ng/mL", "ng/g"),
    invivPK_loq * 1E-3, invivPK_loq)) # mg/L and ug/mL are same scale
# Normalize conc_sd and conc units manually

>>>>

quick_message(c(
  "Modifying Data:",
  "Converting loq units to concentration unit standard mg/L",
  "Converting concentration units to standard mg/L",
  "Converting concentration sd units to the standard mg/L",
  "Keeping concentration values for series 23340 and 23380 to original records"
))
# Normalize LOQ units
cvt_df <- cvt_df %>%
  mutate(invivPK_loq = if_else(
    invivPK_loq_units %in% c("ug/L", "ng/mL", "ng/g"),
    invivPK_loq * 1E-3, invivPK_loq)) %>% 
  mutate(ivivPK_loq_units = "ug/mL") # mg/L and ug/mL are same scale
# Normalize conc_sd and conc units manually
